Contextual Combinatorial Cascading Bandits

### 2016-02-02 contextual combinatorial cascading bandits.tex
modify
update

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent. Each feature vector combines the information of the user and the corresponding base arm. For example, suppose the user at time $t$ is characterized by a feature vector $u_t$ and the base arm $a$ has a feature vector $v_a$, then we can use $x_{t,a} = (u_t, v_a)$ , the concatenation of $u_t$ and $v_a$, as the combined feature vector of base arm $a$ at time $t$. Denote $x_t = (x_{t,a})_{a \in E}$ as all context information at time $t$. Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user. In the cascading feedback models, the user checks from the first item of recommended action and stops at the $\bO_t$-th item under some stopping criterion. For example in recommender systems, the stopping criterion might be that the user finds an attractive item. Then the learning agent observes the weights of first $\bO_t$ base arms in $\bA_t$, denoted by $\bw_t(\ba_k^t), k \leq \bO_t$.

@@

\paragraph{Lipschitz continuity}
The expected reward function $f(A, w)$ is Lipschitz continuous with respect to $w$ together with position discount parameters $\gamma_k, k\leq K$. In particular, there is a constant $B>0$ such that, for any $w,w' \in [0,1]^E$, we have
$$
	|f(A, w) - f(A, w')| \leq B \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|,
$$
where $A = (a_1, \ldots, a_{|A|})$.

@@

		\STATE {//Update statistics}
		\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
		\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
		\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
		\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
		\STATE {$\bbeta_{t}(\delta) \leftarrow R \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
		\ENDFOR {~~$t$}
	\end{algorithmic}
\end{algorithm}

%At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent chooses her action.

@@

@@

In the last experiment, we evaluated $C^3$-UCB on a problem of network routing with the {\it RocketFuel} dataset \cite{spring2004measuring}.

>>>>

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent. Each feature vector combines the information of the user and the corresponding base arm. For example, suppose the user at time $t$ is characterized by a feature vector $u_t$ and the base arm $a$ has a feature vector $v_a$, then we can use $x_{t,a} = u_t v_a^{\top}$ , the outer-product of $u_t$ and $v_a$, as the combined feature vector of base arm $a$ at time $t$. Denote $x_t = (x_{t,a})_{a \in E}$ as all context information at time $t$. Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user. In the cascading feedback models, the user checks from the first item of recommended action and stops at the $\bO_t$-th item under some stopping criterion. For example in recommender systems, the stopping criterion might be that the user finds an attractive item. Then the learning agent observes the weights of first $\bO_t$ base arms in $\bA_t$, denoted by $\bw_t(\ba_k^t), k \leq \bO_t$.

@@

\paragraph{Lipschitz continuity}
The expected reward function $f(A, w)$ is $B$-Lipschitz continuous with respect to $w$ together with position discount parameters $\gamma_k, k\leq K$. More specifically, for any $w,w' \in [0,1]^E$, we have
$$
	|f(A, w) - f(A, w')| \leq B \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|,
$$
where $A = (a_1, \ldots, a_{|A|})$.

@@

Before presenting the algorithm, we explain the main ideas in the design.

@@

		\STATE {//Update statistics}
		\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
		\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
		\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw_t(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
		\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
		\STATE {$\bbeta_{t}(\delta) \leftarrow R \sqrt{\ln(\det(\bV_{t})/(\lambda^d \delta^2))} + \sqrt{\lambda}$ }
		\ENDFOR {~~$t$}
	\end{algorithmic}
\end{algorithm}

@@

In the last experiment, we evaluated $C^3$-UCB on network routing problem with {\it RocketFuel} dataset \cite{spring2004measuring}.
